%%%%
%% Load the class. Put any options that you want here (see the documentation
%% for the list of options). The following are samples for each type of
%% thesis:
%%
%% Note: you can also specify any of the following options:
%%  logo: put a University of Edinburgh logo onto the title page
%%  frontabs: put the abstract onto the title page
%%  deptreport: produce a title page that fits into a Computer Science
%%      departmental cover [not sure if this actually works]
%%  singlespacing, fullspacing, doublespacing: choose line spacing
%%  oneside, twoside: specify a one-sided or two-sided thesis
%%  10pt, 11pt, 12pt: choose a font size
%%  centrechapter, leftchapter, rightchapter: alignment of chapter headings
%%  sansheadings, normalheadings: headings and captions in sans-serif
%%      (default) or in the same font as the rest of the thesis
%%  [no]listsintoc: put list of figures/tables in table of contents (default:
%%      not)
%%  romanprepages, plainprepages: number the preliminary pages with Roman
%%      numerals (default) or consecutively with the rest of the thesis
%%  parskip: don't indent paragraphs, put a blank line between instead
%%  abbrevs: define a list of useful abbreviations (see documentation)
%%  draft: produce a single-spaced, double-sided thesis with narrow margins

\documentclass[msc,cs,deptreport,logo,abbrevs,11pt]{infthesis}

\usepackage[numbers]{natbib}
\usepackage{hyperref}
\usepackage{url}
\usepackage{listings}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[normalem]{ulem}
\usepackage[skins]{tcolorbox}
\usepackage{xspace}\usepackage[inline]{enumitem}
\usepackage{etoolbox}
\usepackage{multirow}

\lstset
{ %Formatting for code in appendix
    language=Python,
    basicstyle=\footnotesize,
    numbers=left,
    stepnumber=1,
    showstringspaces=false,
    tabsize=1,
    breaklines=true,
    breakatwhitespace=false,
}

\newcommand{\rcpt}[1]{\emph{#1}}

\newcommand{\dpy}{dispel4py\xspace}
\newcommand{\Dpy}{Dispel4py\xspace}

\newcommand{\THE}[1]{the #1}

\newcommand{\tesieve}{sieve of Eratosthenes\xspace}
\newcommand{\teSieve}{Sieve of Eratosthenes\xspace}
\newcommand{\ttesieve}{\THE{\tesieve}}
\newcommand{\tsieve}{\tesieve}
\newcommand{\tSieve}{\teSieve}
\newcommand{\ttsieve}{\THE{\tsieve}}
\newcommand{\ttSieve}{\THE{\tSieve}}

\newcommand{\defTerm}[2]{%
  \expandafter\newcommand\csname t#1\endcsname{\emph{#2}\xspace}}

\defTerm{IncDep}{Incremental Deployment}
\defTerm{Incdep}{Incremental deployment}
\defTerm{incdep}{incremental deployment}

\defTerm{DynExp}{Dynamic Expansion}
\defTerm{Dynexp}{Dynamic expansion}
\defTerm{dynexp}{dynamic expansion}

\title{Making \dpy dynamic}
\author{Rui Zhao s1623641}

%% If the year of submission is not the current year, uncomment this line and 
%% specify it here:
% \submityear{1785}

%% Optionally, specify the graduation month and year:
% \graduationdate{February 1786}

%% Specify the abstract here.
\abstract{%
Although workflows and relevant technologies are being used widely, there are still some aspects that current workflow management systems (WMSs) did not cover. The data-streaming style is the future trend but current systems did not fully utilize the properties of data-streaming. We present two extensions, \tincdep and \tdynexp, to \dpy, a data-streaming WMS, to add more dynamics during runtime and enable future extensions and optimizations: \tincdep allows \dpy to incrementally deploy PEs to nodes during runtime rather than at the beginning of the execution; \tdynexp enables \dpy to dynamically manipulate the workflow according to actual needs. We build these two extensions on top of the MPI mapping of \dpy and demonstrate they two extend \dpy at a low cost and scale reasonably. We also show there is space to optimize so the overhead may reduce and these two extensions opens several windows for future extensions and optimizations.
}

\begin{document}
\begin{preliminary}
\maketitle

\begin{acknowledgements}
Many thanks to my supervisor, Prof.\ Malcolm Atkinson, who gave me many initial ideas, helped to improve the assumptions and designs and kindly assisted my write-up for the dissertation; and thanks to Rosa Filgueira, my co-supervisor, who kindly gave me many suggestions about the details and the dissertation thesis. Of course, thanks for the help and teaching of all my previous lecturers and teachers.

I also appreciate the previous work of the researchers in workflow-related technologies for they have enabled this research field and presented many valuable ideas and examples.

Also thanks to the help from many people online who helped me to figure out the usage of some toolkits, as well as the authors of many toolkits, including mpi4py which is one of the basis of our work.
\end{acknowledgements}

\standarddeclaration

%% Finally, a dedication (this is optional -- uncomment the following line if
%% you want one).
% \dedication{To my mummy.}

\tableofcontents

%% If you want a list of figures or tables, uncomment the appropriate line(s)
% \listoffigures
% \listoftables

\end{preliminary}


%%%%%%%%
\include{introduction}
	
\include{terminology}

\include{background}

\include{use_case}
	
\include{incremental_deployment}
	
\include{dynamic_expansion}
	
\include{measurement}

\include{conclusion}

%%%%%%%%
%% Any appendices should go here. The appendix files should look just like the
%% chapter files.
%\appendix
%\include{appendix1}
%% ... etc...

%% Choose your favourite bibliography style here.
%\bibliographystyle{apalike}
\bibliographystyle{plainnat}

%% If you want the bibliography single-spaced (which is allowed), uncomment
%% the next line.
% \singlespace

%% Specify the bibliography file. Default is thesis.bib.
\bibliography{dissertation_bib,sieve}

%% ... that's all, folks!
\end{document}
